---
title: "Codebook"
output: html_document
date: "2022-09-22"
author: Steele Fredricks 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data set

Immunization expenditure data

## Description

Immunization expenditure data provide detailed analyses on country-level expenditure and financial flows for immunization. These data sections are collected annually through the WHO/UNICEF joint reporting mechanism. These values show the relationship between the amount of money funded by a country for immunization and the population who is properly immunized.

## Format

ISO_3\_CODE: Country name

WHO_REGION: World Health Orginization Region

YEAR: 2017-2021

INCODE: Second half of postal code

DESCRIPTION: Questions about the country and goverment and how they relate with immunizations

INDSORT: Value

## Overview

The Data set includes values based of off questions asked by the World Health Orginization to understand Govermental Policies on Immunizations and how they are assesed by region.

## Source

World Health Orginization (WHO) <https://www.who.int/>

```{r}

```
